Experiments on ANTS Algorithms Without Communication

### 2014-12-09 paper/draft.tex
adding images and graphs

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amsthm}
\usepackage{subfigure}
%\usepackage{caption} 
%\usepackage{subcaption}
%\usepackage{cite}
\usepackage{hyperref}
\usepackage{url}
\usepackage{clrscode4e}
\urlstyle{same}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

For the Harmonic Search algorithm, we were only able to test it for $D = 10$, since for higher values of $D$, the algorithm became prohibitively expensive. We varied $k$ from 10 to 200 inclusive in intervals of 10 as with Lines and Spiral, and we tested each for 100 times, with randomly placed treasures.

@@

After running the experiments on all five algorithms (Spiral non-uniform in $k$, Spiral uniform in $k$,

\subsection{Interpretation}

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amsthm}
\usepackage[tight,footnotesize]{subfigure}
%\usepackage{caption} 
%\usepackage{subcaption}
%\usepackage{cite}
\usepackage{hyperref}
\usepackage{url}
\usepackage{clrscode4e}
\urlstyle{same}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

For the Harmonic Search algorithm, we were only able to test it for $D = 10$, since for higher values of $D$, the algorithm became prohibitively expensive. We varied $k$ from 10 to 200 inclusive in intervals of 10 as with Lines and Spiral, and we tested each for 100 times, with randomly placed treasures. For the Harmonic Search algorithm we let $\delta = 1$. For the Lines algorithm, we let $K = 6$.

When done with all the iterations, we compute the average time per 100 experiments and assume that this is the expected value.

@@

After running the experiments on all six algorithms (Spiral non-uniform in $k$, Spiral uniform in $k$, Lines non-uniform in $D$, Lines uniform in $D$, but not in $n$, Lines uniform in $n$ and $D$, and Harmonic Seach).

\subsubsection{Non-uniform in $k$} For non-uniform in $k$ algorithms, we assume that the expected runtime of the algorithms is given by the following formula
\[ E[T] = c_1 + c_2 / k \]
Where we are keeping $D = 40$. So we are looking to compute the constants $c_1$ and $c_2$ for the Spiral and Lines algorithm. Figure~\ref{nonuniformresultsone} and Figure~\ref{nonuniformresultstwo} shows the $k$ being graphed against $k * E[T]$, which we expect to be linear with solve $c_1$ and intercept $c_2$. Using linear regression, we are able to estimate the values of $c_1$ and $c_2$. 
\begin{center}
\begin{tabular}{l | c c}
\text{Algorithm} & $c_1$ & $c_2$ \\
\hline
\text{Spiral} 	   &147 & 21567 \\
\text{Lines}	   & 896 & 32730 
\end{tabular}
\end{center}

\begin{figure}
\centering
\label{nonuniformresultsone}
\includegraphics[width=0.5\linewidth]{FKLS1.png}
\caption{Spiral algorithm non-uniform in $k$, $kE[T]$ is the $y$-axis and $k$ is in the $x$-axis}
\end{figure}

\begin{figure}
\centering
\label{nonuniformresultstwo}
\includegraphics[width=0.5\linewidth]{LinesUniformInD.png}
\caption{Lines algorithm non-uniform in $k$, $kE[T]$ is the $y$-axis and $k$ is in the $x$-axis}
\end{figure}

\subsubsection{Uniform in $k$} For uniform in $k$ algorithms, we assume that the expected runtime of the algorithms is given by the following formula
\[ E[T] = f(\log k)(c_1 + c_2 / k) \]
Where we set $f(x) = x^2 + 1$. This satisfies all our constraints from the theorems in the paper.
Again, we keep $D = 40$ and we want to compute the constants $c_1$ and $c_2$ for the Spiral and Lines algorithm. Figure~\ref{uniformresultsone} and Figure~\ref{uniformresultstwo} shows the $k$ being graphed against $k * E[T]/f(\log k)$, which we expect to be linear with solve $c_1$ and intercept $c_2$. Using linear regression, we are able to estimate the values of $c_1$ and $c_2$. 
\begin{center}
\begin{tabular}{l | c c}
\text{Algorithm} & $c_1$ & $c_2$ \\
\hline
\text{Spiral} 	   &222 & 19954 \\
\text{Lines}	   & 284 & 76762 
\end{tabular}
\end{center}

\begin{figure}
\centering
\label{uniformresultsone}
\includegraphics[width=0.5\linewidth]{FKLS2.png}
\caption{Spiral algorithm uniform in $k$, $kE[T]/f(\log k)$ is the $y$-axis and $k$ is in the $x$-axis}
\end{figure}

\begin{figure}
\centering
\label{uniformresultstwo}
\includegraphics[width=0.5\linewidth]{LinesUniformInAll.png}
\caption{Lines algorithm non-uniform in $k$, $kE[T]/f(\log k)$ is the $y$-axis and $k$ is in the $x$-axis}
\end{figure}

\subsubsection{Interpretation}
This shows that in fact, when only analyzing runtime. The Spiral algorithm performs better than the Lines algorithm in both uniform and non-uniform cases. This of course, was expected, since the Lines algorithm optimizes for memory.

Some interesting thing we noted is that when running the Lines algorithm in the non-uniform flavour in $D$, we noted that there were lower order terms which were important in the runtime. Figure~\ref{nonuniforminD} and Figure~\ref{nonuniforminDtwo} show how there are lower order terms that are hidden in the asymptotics that do make a difference in the experiments for small $k$. In fact, the assumption that $E[T] = c_1 + c_2 / k$ gives us the graph Figure~\ref{nonuniforminD} being a line, whereas the assumption $E[t] = c_1/ k + c_2 / k^2$ gives us the graph Figure~\ref{nonuniforminDtwo} being a line, which is much more accurate.

\begin{figure}
\centering
\label{nonuniforminD}
\includegraphics[width=0.5\linewidth]{LinesNonUniformnT.png}
\caption{Lines algorithm non-uniform in $D$, $kE[T]$ is the $y$-axis and $k$ is in the $x$-axis}
\end{figure}

\begin{figure}
\centering
\label{nonuniforminDtwo}
\includegraphics[width=0.5\linewidth]{LinesNonUniformn2T.png}
\caption{Lines algorithm non-uniform in $D$, $k^2E[T]$ is the $y$-axis and $k$ is in the $x$-axis}
\end{figure}

\subsection{Harmonic Search}

We assume that the expected value for the runtime of the Harmonic Search algorithm is given by the following formula
\[ E[T] = c_1 + c_2 / k \]
and we compute the constants $c_1$ and $c_2$. We get that for $D=10$, $c_1 = 148$ and $c_2 = 2319$. Figure~\ref{harmonic}

\begin{figure}
\centering
\label{harmonic}
\includegraphics[width=0.5\linewidth]{Harmonic.png}
\caption{Harmonic Search algorithm, $kE[T]$ is the $y$-axis and $k$ is the $x$-axis.}
\end{figure}
